### 2016-03-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Smoothen out Truncation text

\researchBasedOn[This section]{Lumori2014TIM}
\TODO{labels into standardized form}

\subsection{Introduction}

This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}. 
Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.

@@

Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.

In this section, however, a nonparametric technique is developed, and
formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:nparam:trunc:LPM:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}. As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the \gls{LPM}.

@@

\section{Smoothing the \gls{FRF} estimate}\label{se:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from \secref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.

\item Assuming that the impulse response decays with the passing of time, the noise is bound to predominate after a certain time interval. 
In particular, when $t > \truncTime$, the impulse response has decayed below the noise floor.
In \secref{sec:nonparametric:truncation:Ftest} and \secref{sec:nonparametric:truncation:exponentialFit}, two approaches are introduced to estimate $\truncTime$.

@@

\TODO{write about boxcar average, add reference}
\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of the impulse response of a  boxcar averager.}
\end{figure}

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
         \caption{RMSE vs $\truncTime$ for boxcar}
\end{figure}

\TODO{RMSE vs $\truncTime$ for boxcar figure}

>>>>

\label{sec:nonparametric:truncation}
\researchBasedOn[This section]{Lumori2014TIM}
\TODO{labels into standardized form}

% This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
% The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
% Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}. 
% Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
% Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.

@@

Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}. 
In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}. As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\bigO{{N}^{-1}}$, for Hanning windowing, to $\bigO{{N}^{-3}}$ or better, for the \gls{LPM}.

@@

\section{Smoothing the \gls{FRF} estimate}
\label{se:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from \secref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.

\item Assuming that the impulse response decays with the passing of time, the noise is bound to predominate after a certain time interval. 
In particular, when $t > \truncTime$, the impulse response has decayed below the noise floor.
In \secref{sec:nonparametric:truncation:ftest} and \secref{sec:nonparametric:truncation:exponentialfit}, two approaches are introduced to estimate $\truncTime$.

@@

\TODO{write about boxcar average, add reference}

\begin{align}
  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
\end{align}

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of the impulse response of a  boxcar averager.}
\end{figure}

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
         \caption{RMSE vs $\truncTime$ for boxcar \TODO{better caption}}
\end{figure}
